Bare Demo of IEEEtran.cls for Journals

### 2019-12-13 2-oracle/report/paper.tex
include ensemble in network model

@@

% ljy
\subsection{Ensemble of Two Methods}
To improve the performance of the model, we add an ensemble network for CNN. (UNFINISHED)

@@

\begin{table}[h]
	\centering
	\caption{Accuracy for Different Models}
	\label{tab:result}
	\begin{tabular}{|c|c|c|}
		\hline
		                            & Cat10  & Cat40  \\\hline
		DNN ($\delta=0.5$)          & 0.8475 & 0.5275 \\\hline
		DNN Ensemble ($\delta=0.5$) & 0.8000 & 0.56   \\\hline
		TM ($\Delta=150$, NMSE)     & 0.7575 & 0.6125 \\\hline
		TM ($\Delta=150$, NCCOR)    & 0.8475 & 0.7000 \\\hline
		TM Ensemble ($\Delta=?$)    & ?      & ?      \\\hline
	\end{tabular}
\end{table}

Table~\ref{tab:result} shows the accuracy of different models wrt. the test set.

>>>>

It is possible to improve the performance of DNN method by building an ensemble of the Cat10 network model and Cat40 network model so that we can cancel some errors in one network with the support of another.
We use the outputs from two networks as the inputs to another dense layer to further classify samples based on the first stage results.
We train the extra dense layer still using the train samples.
However, the performance of the ensemble models does not improve wrt. the original DNN.

@@

@@

\begin{table}[h]
	\centering
	\caption{Accuracy for Different Models}
	\label{tab:result}
	\begin{tabular}{|c|c|c|}
		\hline
		                            & Cat10  & Cat40  \\\hline
		DNN ($\delta=0.5$)          & \textbf{0.8475} & 0.5275 \\\hline
		DNN Ensemble ($\delta=0.5$) & 0.8000 & 0.56   \\\hline
		TM ($\Delta=150$, NMSE)     & 0.7575 & 0.6125 \\\hline
		TM ($\Delta=150$, NCCOR)    & \textbf{0.8475} & \textbf{0.7000} \\\hline
	\end{tabular}
\end{table}

Table~\ref{tab:result} shows the accuracy of different models wrt. the test set.
It turns out that the DNN is no better than template matching in the case of micro category classification due to its sensitiveness to noises.
